An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-10 paper.tex
First stab at data limitations, closes #41.

>>>>

\section*{Data Limitations}
%
The data is provided in good faith with great attention to detail. The
following list gives various notes and warnings about the data that should be
taken into account when making use of it.
%
\begin{itemize}
  \item Be sure to read the notes in each meta data file for details about
    possible anomalies in that particular trial.
  \item The subject identification number 0 stands for "no subject" and was
    used whenever data was collected from the system with no subject on the
    treadmill, for example during the trials that were intended to be used for
    inertial compensation purposes if the treadmill was moving. These trials
    play through the exact protocol as those with a human subject and the
    matching trials are indicated in the meta data.
  \item Trials 1 and 2 were not recorded as part of this study. Those trial
    identification numbers were reserved for early data exploration from data
    collected in other studies.
  \item Trials 37, 38, and 39 do not exist. The numbers were accidentally
    skipped.
  \item Trials 9, 10, and 11 used a slightly different event definition where the
    calibration poses were not explicitly tagged by an event, yet the protocol
    was the identical to the following trials.
  \item During trials 9-15 we used wooden blocks to fix the treadmill to the
    concrete floor to eliminate the treadmill's lowest factory vibration mode
    (~5 hz). But these blocks seem to have corrupted the force plate
    measurements by imposing undue stresses on the system. The force plate
    measurements should not be used from these trials, but the marker data is
    fine.
  \item We did not record unloaded compensation trials for trials 9-15.
    Regardless, they would be useless due to the previous point.
  \item Trials 6-8 use an early experimental protocol which divided the
    perturbation sections into three sections: longitudinal perturbations,
    lateral perturbations, and a combination of each. We then learned the
    treadmill had a low vibrational mode which significantly affects the force
    plate measurements. The force measurements during these trials are
    corrupted by this vibrational mode and should be used with caution or not
    at all.
  \item Trials 6-8 use a XX lower body marker set only.
  \item The ankle joint torques computed from subject 9's data in trials 25-27
    are abnormal and should be used with caution or not at all. We were not
    about to locate the source of the error, but it is likely related to the
    force calibration.
\end{itemize}
